Parity games in pushdown systems with parameters

### 2023-06-20 reachability/article.tex
up

\keywords{Parity Games, Computational Complexity, Pushdown systems, Pebble Alternating Two Way Automata}

@@

\begin{abstract}
	We investigate the decidability and complexity of
	parity games over an extension of pushdown systems.
	More specifically, we consider parameters pushdown systems, in
	which parameters can be instantiated to some word over a stack alphabet,
	and compared against the current stack content.
	We determine decidability of the problem, and provide a nonelementary lower bound. 
\end{abstract}

>>>>

\keywords{Parity Games, Computational Complexity, Pushdown systems}

@@

\begin{abstract}
	We investigate the decidability and complexity of
	parity games over an extension of pushdown systems.
	More specifically, we consider parameters pushdown systems, in
	which parameters can be instantiated to some word over a stack alphabet,
	and compared against the current stack content.
	We determine the problem
	belongs to $(n+1)$-$\EXP$ in case the number of parameters
$n$ is fixed, and provide a nonelementary lower bound for the general case. 
\end{abstract}
